Make a README

### 2025-02-12 data.qmd
Be explicit about what renv::snapshot() does
Don't run code unnecessarily
Clarify code comments

vars <- c(
  species = "a character string denoting penguin species",
  island = "a character string denoting island in Palmer Archipelago, Antarctica",
  bill_length_mm = "a number denoting bill length (millimeters)",
  bill_depth_mm = "a number denoting bill depth (millimeters)",
  flipper_length_mm = "an integer denoting flipper length (millimeters)",
  body_mass_g = "an integer denoting body mass (grams)",
  sex = "a character string denoting penguin sex",
  year = "an integer denoting the study year"
)

vals <- list(
  species = c(
    Adelie = "Pygoscelis adeliae",
    Gentoo = "Pygoscelis papua",
    Chinstrap = "Pygoscelis antarcticus"
  )
)
```
``````

@@

```{r}
#| label: "data-citation"
#| output: false

@@

Having added the data and its documentation,
one can view and record the utilized packages with `renv`:

>>>>

# Store the description of variables
vars <- c(
  species = "a character string denoting penguin species",
  island = "a character string denoting island in Palmer Archipelago, Antarctica",
  bill_length_mm = "a number denoting bill length (millimeters)",
  bill_depth_mm = "a number denoting bill depth (millimeters)",
  flipper_length_mm = "an integer denoting flipper length (millimeters)",
  body_mass_g = "an integer denoting body mass (grams)",
  sex = "a character string denoting penguin sex",
  year = "an integer denoting the study year"
)

# Store the description of variable values
vals <- list(
  species = c(
    Adelie = "Pygoscelis adeliae",
    Gentoo = "Pygoscelis papua",
    Chinstrap = "Pygoscelis antarcticus"
  )
)
```
``````

@@

```{r}
#| label: "data-citation"
#| eval: false

@@

Having added the data and its documentation,
one can view and record the utilized packages with `renv`,
thus bringing the project into a consistent state:

### 2025-02-12 make_readme.qmd
Clarify code comments

# Find all dependencies
deps <- renv::dependencies()$Package |>
   unique() |>
   pak::pkg_deps(dependencies = NA) |>
   getElement("package")

# Identify the system dependencies
pak::pkg_sysreqs(deps)
```

>>>>

# Find all R package dependencies
deps <- renv::dependencies()$Package |>
   unique() |>
   pak::pkg_deps(dependencies = NA) |>
   getElement("package")

# Identify their system dependencies
pak::pkg_sysreqs(deps)
```
